### 2021-03-27 Chapter-3/Chapter-3.tex
Updates from Overleaf

\chapter{Fast and Precise Side-channel Vulnerability Detection}\label{chapter3}
\section{Problem}
Side-channel attacks infer sensitive information such as cryptographic keys, personal data from software products unconsciously. As we discuss in \S\ref{chapter1} and \S\ref{chapter2}, patching software are usually easier than adopting new hardware to defend against side-channel attacks.

>>>>

\chapter{Fast and Precise Side-channel Vulnerability Detection}\label{chapter3}
\section{Problem}
Side-channel attacks infer sensitive information such as cryptographic keys, personal data from software products unconsciously. As we discuss in \S\ref{chapter1} and \S\ref{chapter2}, patching leakage sites in software is usually easier than adopting new hardware to defend against side-channel attacks. In order to eliminate those leakage sites, the first step is finding those sites.

Performance.

Precision.
